### 2016-05-20 presentations/damop-2016/setup.tex
[presentations/damop-2016] rotate the plot

>>>>

\begin{frame}
  \begin{tikzpicture}
    \visible<2-3>{
      \shade[shading=radial,yscale=1,fill opacity=0.6,
      inner color=red]
      plot[draw,samples=200,domain=-3:3] function {sqrt(0.0025 + x**2 / 10)}
      -- plot[draw,samples=200,domain=3:-3] function {-sqrt(0.0025 + x**2 / 10)};
      \path (2.5, 0) node {Tweezer};
    }
    \visible<1-2>{
      \fill[orange,opacity=0.8,path fading=glow fading] (0,0) circle (1.5);
    }
    \visible<3>{
      \path (0, 1.5) node[left,align=center] {Imaging\\beams};
      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=90}]
      (-1.5, -0.2) rectangle (1.5, 0.2);
      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=40}]
      (-2, -0.2) rectangle (2, 0.2);
    }
    \visible<2-3>{
      \fill [blue,path fading=glow fading] (0,0) circle (0.08);
    }
  \end{tikzpicture}
\end{frame}
